---
title: "importThermoEIA"
author: "Lillian Gorman Sanisaca, Andrew Halper"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# Section 1: The importThermoEIA package
The importThermoEIA package pulls data on thermoelectric plants,
including forms 923, 860, 767, 906/920, and 759 from the [EIA web
site](https://www.eia.gov/electricity/); and formats the data in a
standard format, including consistent table and column names,
regardless of the year in which the data was reported. This package
addresses one of the main challenges of working with EIA data through
time, which is the variability in naming conventions of file, sheet,
and column names in the EIA forms. The importThermoEIA package
includes tools to assist the user in developing crosswalks between the
names used by the EIA and the scripts that use the data. The primary
use of the importThermoEIA package is to format EIA data to be used by
the EIAplantAssociation and condenserDuty packages. However, functions
in importThermoEIA are general enough to be used to format EIA data
for use in other custom scripts designed by the user.

## Section 1.1: Required Software and Dependencies
The importThermoEIA package must be run on an R version equal to or
later than
[4.0](https://cran.microsoft.com/snapshot/2021-01-17/bin/windows/base/old/4.0.0).
Download the latest version of [R for
Windows](https://cran.r-project.org/bin/windows/base/). An
installation of Rtools (either
[rtools40](https://github.com/r-windows/rtools-installer/releases/download/2022-02-06/rtools40-x86_64.exe)
for R version 4.0.x through 4.1.x or [Rtools42 for
Windows](https://cran.microsoft.com/bin/windows/Rtools/rtools42/rtools.html)
for R version 4.2.x is required to install dependency packages.
Microsoft Excel is also required. The following dependency R packages
listed in the [`DESCRIPTION`](https://github.com/rniswon/Thermoelectric/blob/master/importThermoEIA/DESCRIPTION)
file will be installed when importThermoEIA is installed:

1. [dplyr](https://cran.r-project.org/web/packages/dplyr/index.html)
2. [foreign](https://cran.r-project.org/web/packages/foreign/index.html)
3. [knitr](https://cran.r-project.org/web/packages/knitr/index.html)
4. [magrittr](https://cran.r-project.org/web/packages/magrittr/index.html)
4. [openxlsx](https://cran.r-project.org/web/packages/openxlsx/)
5. [readxl](https://cran.r-project.org/web/packages/readxl/index.html)
6. [rmarkdown](https://cran.r-project.org/web/packages/rmarkdown/index.html)
7. [testthat](https://cran.r-project.org/web/packages/testthat/index.html)
    
## Section 1.2: How to Load the importThermoEIA Package
To load the importThermoEIA package the user must use a method that
installs R packages from [GitHub](https://github.com/) like
`remotes::install_github()`. The remotes package must be installed
first, then the importThermoEIA package using the code below.  Note
that the `subdir` argument is necessary to load this package using
`remotes::install_github()`. This is a one-time process for each
version of R, or version of the importThermoEIA package. After the
importThermoEIA package is installed, you can use it like any other R
package with `library(importThermoEIA)`.

```{r, echo=TRUE, eval=FALSE}
# install the remotes package (one-time process)
install.packages("remotes")

# install the importThermoEIA package (one-time process)
remotes::install_github(
  repo = "https://github.com/rniswon/Thermoelectric",
  subdir = "importThermoEIA", build_vignettes = T, upgrade = "never"
)

# load the importThermoEIA package (necessary each time the package is
# used in a given R session)
library(importThermoEIA)
```

When the importThermoEIA package is installed, all dependency packages
from [Section 1.1](#section-1.1-required-software-and-dependencies)
will be installed and the process will take a few minutes, but once
the package is installed all dependencies will load with
`library(importThermoEIA)`.

# Section 2: Using the importThermoEIA Package
The importThermoEIA package is designed to be used on EIA data from
2000 forward, however, only data from 2008 forward can be used in the
`EIAplantAssociation` and condenserDuty packages. For each year, the
following EIA forms are imported. All files associated with each form
will be imported into a single directory labeled with the year in
which the data was reported and will be accessible to the user outside
of the R environment.

1. 2000-forward: [Form-860](https://www.eia.gov/electricity/data/eia860/)
2. 2008-forward: [Form-923](https://www.eia.gov/electricity/data/eia923)
3. 2001-2007: [Form-906/920](https://www.eia.gov/electricity/data/eia923)
4. 2000-2005: [Form-767](https://www.eia.gov/electricity/data/eia767)
5. 2000: [Form-759](https://www.eia.gov/electricity/data/eia923)

## Section 2.1: Pull EIA Data From the Web Using `eia_webpull()`
The first step in developing EIA tables for use in R is to pull the
data directly from the [EIA web site](https://www.eia.gov/electricity/).
The `eia_webpull()` function is used as follows:

```{r, echo=TRUE, eval=FALSE}
# directory where raw EIA pulled from the web will be saved
EIAsaveOut <- "D:/"

# specify which year's data to pull (subdirectory within EIAsaveOut
# will be labeled with the eia_year)y
eia_year <- 2020

# pull and save EIA data from the web
eia_webpull(eia_year, EIAyearSave)
```

## Section 2.2: Developing an EIA-code Crosswalk to Assign Consistent Names to EIA Data
One of the biggest challenges to working with EIA data is the lack of
consistency in file, sheet, and column naming conventions through
time. While much of the data content remains the same, the file,
sheet, and column names vary widely. The importThermoEIA package
employs a crosswalk method to conform names of tables and columns of
EIA data so that the same R scripts can be used to analyze data from
2000 forward without customizing the analysis scripts for each year.
A crosswalk is a table that assigns a `scriptTableName` and
`scriptColname` to a given column of EIA data (`InputColumnName`) in a
given EIA sheet (`InputSheetName`) for Microsoft Excel files in a
given EIA file (`InputFile`) in a row-wise manner.

## Section 2.3: The `crosswalk2015` Data Object
An example crosswalk is included in the importThermoEIA package called
crosswalk2015. This example crosswalk was build for the year 2015 and
contains all required data for the EIAplantAssociation and
condenserDuty packages. The `crosswalk2015` data frame can be accessed
using the standard R data loading procedure shown below.

```{r, echo=TRUE, eval=FALSE}
# load the example crosswalk (will be called 'crosswalk2015' in the R
# environment)
#
# the importThermoEIA package must be available to load the data
#
# use library(importThermoEIA) to make the importThermoEIA package
# available in the R environment
data("crosswalk2015")

# save example crosswalk externally
#
# path to output example crosswalk as .xlsx file for external viewing
outCrossPath <- "./crosswalk2015.xlsx"
openxlsx::write.xlsx(crosswalk2015, file = outCrossPath, row.names = FALSE)

```

The `crosswalk2015` data object is a data frame with 210 rows and 8
columns. The column descriptions are given in the table below.
Columns flagged with `TRUE` in the `Required Column` *must* be present
in a crosswalk to run importThermoEIA functions.

```{r Table1, echo=FALSE}
table1 <- structure(list(`Column Name` = c(
  "`InputFile`", "`InputSheetName`",
  "`InputSheetDescription`", "`InputColumnName`", "`InputColumnDescription`",
  "`scriptImportFunc`", "`scriptTableName`", "`scriptColnames`"
), `Column Description` = c(
  "A character vector of EIA file names for the year 2015",
  "A character vector of Excel sheet names for the year 2015",
  paste0(
    "A character vector of EIA data descriptions of a given Excel ",
    "sheet for the year 2015"
  ),
  "A character vector of EIA column names for the year 2015",
  paste0(
    "A character vector of EIA data descriptions of a given column ",
    "for the year 2015"
  ),
  paste0(
    "A character vector of required import functions to be used if ",
    "preparing data for the plant_association and/or condenserDuty ",
    "packages"
  ),
  paste0(
    "A character vector of required tables to be used if preparing ",
    "data for the plant_association and/or condenserDuty packages"
  ),
  paste0(
    "A character vector of required column names to be used if ",
    "preparing data for the plant_association and/or condenserDuty ",
    "packages"
  )
), `Required Column` = c(
  "TRUE", "TRUE", "FALSE", "TRUE", "FALSE",
  "TRUE (column must be present, but content can be blank)", "TRUE",
  "TRUE"
)), row.names = c(NA, 8L), class = "data.frame")

knitr::kable(table1,
  caption = "Table 1: Column Descriptions for crosswalk2015 data object."
)
```

At first glance this table seems daunting, but there are built-in
tools to aid the user in developing a custom crosswalk.

If developing a crosswalk for use in the EIAplantAssociation and
condenserDuty packages, all values from the `scriptTableName` and
`scriptColnames` found in the `crosswalk2015` data object *must* be
present with the exception of the values shown below which are not
critical to the `EIAplantAssociation` or condenserDuty packages.
These exceptions are not always present in years prior to 2015, but it
is important to note that *if* the data are available, these exception
rows should be included in the crosswalk. The `FirstYearRequired`
column indicates the earliest year in which a column is required, if
`NA` the column is never required.

```{r echo=FALSE,eval=TRUE}
table2 <- structure(list(scriptTableName = c(
  "`bogen`", "`bocoo`", "`gen_860`",
  "`boilerDesignData`", "`cooling`", "`cooling`", "`cooling`", "`cooling8D`",
  "`cooling8D`", "`cooling8D`", "`cooling8D`", "`cooling8D`"
), scriptColnames = c(
  "`Plant.Name`",
  "`Plant.Name`", "`Technology`", "`Plant.Name`", "`Plant.Name`",
  "`Water.Source.Code`", "`Water.Type.Code`",
  "`Month`", "`Withdrawal_MG`", "`Discharge_MG`",
  "`Consumptive_MG`", "`Service_hrs`"
), FirstYearFound = c(
  NA, NA,
  "2014", NA, NA, "2011", "2011", "2010", "2012", "2012", "2012",
  "2010"
)), row.names = c(NA, -12L), class = "data.frame")

knitr::kable(
  table2,
  caption = paste0(
    "Table 2: Rows in the crosswalk2015 object *not* required for all ",
    "years to import data for use in the EIAplantAssocation and/or ",
    "condenserDuty packages"
  )
)
```

If `prepCondenserDuty = TRUE` the `import_EIAData()` function will
verify whether all required data for the EIAplantAssociation and
condenserDuty packages is present. If there are missing
`scriptTableNames`, `scriptColnames`, or `scriptImportFunc` required
for the EIAplantAssociation and condenserDuty packages, the user
will see this display in the console:

<span style="color: red; font-family: monospace;">The following required
tables/columns are NOT present</span>

```
                                                   InputSheetDescription       InputColumnDescription
1 Form EIA-860 Data - Schedule 3, 'Generator Data' (Operable Units Only)                         <NA>
2                 Form EIA-860 Data - Schedule 6D, 'Cooling System Data' Type of cooling water source
3                 Form EIA-860 Data - Schedule 6D, 'Cooling System Data'        Type of cooling water
4                            Form EIA-923, Power Plant Operations Report                         <NA>
5                            Form EIA-923, Power Plant Operations Report                         <NA>
6                            Form EIA-923, Power Plant Operations Report                         <NA>
7                            Form EIA-923, Power Plant Operations Report                         <NA>
8                            Form EIA-923, Power Plant Operations Report                         <NA>
       scriptImportFunc scriptTableName    scriptColnames
1 import_generator_data         gen_860        Technology
2     import_coolingSys         cooling Water.Source.Code
3     import_coolingSys         cooling   Water.Type.Code
4             import_8D       cooling8D             Month
5             import_8D       cooling8D     Withdrawal_MG
6             import_8D       cooling8D      Discharge_MG
7             import_8D       cooling8D    Consumptive_MG
8             import_8D       cooling8D       Service_hrs
```
<span style="color: red; font-family: monospace;">EIAplantAssociation and/or
consenserDuty analysis CANNOT be completed</span>

The user must then edit the crosswalk to include the missing values and run
`import_EIAData()` again.

## Section 2.4: Using the `import_EIAData()` Function to Build a Crosswalk and Format Data
The `import_EIAData()` function is used to both build a crosswalk and
format the data once the crosswalk is complete. There are two possible
paths to begin the crosswalk building process: (1) begin with the
`crosswalk2015` data object, and (2) begin with a crosswalk file
developed by the user in .xlsx format. Below are the arguments of the
`import_EIAData()` function.

```{r eval=TRUE,echo=FALSE}
table3 <- structure(list(`Function Argument` = c(
  "`path_InputData_Metafile`",
  "`path_EIAInputData`", "`outputCSV`", "`path_outputCSV`",
  "`useStandardCrosswalk`", "`prepCondenserDuty`", "`eia_year`"
), Description = c(
  paste0(
    "Character string indicating path to crosswalk file must be in ",
    ".xlsx format. If `useStandardCrosswalk == TRUE` then this is the ",
    "path to which the crosswalk will be saved for further edit by the ",
    "user."
  ),
  paste0(
    "Character string indicating directory in which EIA data files ",
    "have been extracted from ZIP files. If using the `eia_webpull()` ",
    "function, the directory will be specified by the `eia_year`."
  ),
  paste0(
    "`TRUE`/`FALSE` indicating whether or not to save formatted data as ",
    "individual CSV files"
  ),
  "Path to directory in which to save the formatted EIA data as CSV files.",
  paste0(
    "`TRUE`/`FALSE` indicating whether the `data(\"crosswalk2015\")` file ",
    "should be used to start the crosswalk development process. After ",
    "the first run the resulting crosswalk will be saved as ",
    "`path_InputData_Metafile`. Subsequent runs of `import_EIAData` ",
    "should have `useStandardCrosswalk` as `FALSE`."
  ),
  paste0(
    "`TRUE`/`FALSE` indicating whether checks should be made for ",
    "data required to execute the `EIAplantAssocation` and/or ",
    "condenserDuty packages"
  ),
  paste0(
    "A numeric value indicating the year of EIA data being ",
    "formatted. *Only* required if `prepCondenserDuty` is `TRUE`."
  )
)), row.names = c(NA, 7L), class = "data.frame")

knitr::kable(
  table3,
  caption = "Table 3: import_EIAData() function argument descriptions"
)
```

### Section 2.4.1: Run `import_EIAData()` Using the `crosswalk2015` Data Object
To run `import_EIAData()` using the `crosswalk2015` object, set the
`useStandardCrosswalk` argument to `TRUE` and specify the
`path_InputData_Metafile` as the file to which the crosswalk will be
saved for manual edits by the user.

```{r, eval=FALSE, echo=TRUE}
# run the import_EIAData() function for the first time using the
# crosswalk2015 object

# path to crosswalk being used to start
path_InputData_Metafile <-
  paste0(repoPath, "./newCrosswalk2020.xlsx")

# path to EIA raw data
#
# path should be to directory with extracted data from ZIP files
# (created by eia_webpull)
path_EIAInputData <- paste(EIAyearSave, eia_year, sep = "/")

# if saving formatted tables as csv set outputCSV <- TRUE; otherwise
# outputCSV <- FALSE
outputCSV <- TRUE

# path to save formatted tables in CSV form (set
# path_outputCSV <- NA, if outputCSV <- FALSE)
path_outputCSV <- path_EIAInputData

# execute import_EIAData for the first time
inputData.list <-
  import_EIAData(path_InputData_Metafile,
    path_EIAInputData,
    outputCSV,
    path_outputCSV,
    # this should only be used on the first run of the import_EIAData function
    useStandardCrosswalk = TRUE,
    # TRUE if prepping data for EIAplantAssociation and/or condenserDuty
    # packages
    prepCondenserDuty = TRUE,
    # only required if prepCondenserDuty = TRUE
    eia_year = 2020
  )
```

If running the year 2015, no edits to the `crosswalk2015` will be
required and the `import_EIAData()` function will return a list object
with all tables from `scriptTableName` included. It is important to
mention that all columns of any given `InputSheetName` will be
accessible, but *only* columns listed in `InputColumnName` will be
standardized and replaced by values in `scriptColnames`. When run on
2015 data, using the `crosswalk2015` data object as the crosswalk, the
`import_EIAData()` function will output the following in the console:

```
> inputData.list<-import_EIAData(path_InputData_Metafile,path_EIAInputData,outputCSV,path_outputCSV)
[1] "bogen"
Test passed
[1] "bocoo"
Test passed
[1] "gen_860"
Test passed
[1] "retiredGenerators"
[1] "generation.data"
Test passed
[1] "boilerFuelData"
Test passed
[1] "gen_fuel_data"
Test passed
[1] "boilerDesignData"
Test passed
[1] "cooling"
Test passed
[1] "plantInfo"
Test passed
[1] "cooling8D"
Test passed
```

When developing a crosswalk for year different from 2015 using the
`crosswalk2015` data object, you will likely see the following in the
console:

```
> inputData.list<-import_EIAData(path_InputData_Metafile,path_EIAInputData,outputCSV,path_outputCSV)
[1] "Please review the Input Data Metafile for highlighted errors."
```

In this case, the `import_EIAData()` function has modified the
crosswalk to highlight data that it was unable to find in
`path_EIAInputData`, and saved the resulting file to the location
specified by `path_InputData_Metafile`. The `import_EIAData()`
function works from left to right attempting to match what is in the
crosswalk to what is in the `path_EIAInputData` directory. With each
run of `import_EIAData()`, the user should open and resolve all
highlighted values. For example, if running 2020 and the `InputFile`
`6_1_EnviroAssoc_Y2015.xlsx` cannot be found, the user should look at
the `InputSheetDescription`, and attempt to locate the data within the
`path_EIAInputData` directory. In the case of 2020 the `InputFile`
value should be changed to `6_1_EnviroAssoc_Y2020.xlsx`, but for the
year 2008 it would be `F860_SCHEDULE6_Y08.xls`. All `InputFile` values
should be present in the `path_EIAInputData` directory.

Once all highlighted values have been resolved, *save and close* the
crosswalk file. Once the file is closed the user should run
`import_EIAData()` again, with the `useStandardCrosswalk` argument set
to `FALSE.` If the crosswalk file has not been closed the function
will return an error. If the `useStandardCrosswalk` argument is not
set to `FALSE`, the edits that the user made to the
`path_InputData_Metafile` will be overwritten with the original
`crosswalk2015` data object. Use the following to run all subsequent
runs of the `import_EIAData()` function:

```{r, eval=FALSE, echo=TRUE}
# execute import_EIAData for every time except the first time
inputData.list <-
  import_EIAData(path_InputData_Metafile,
    path_EIAInputData,
    outputCSV,
    path_outputCSV,
    # on every run but the first useStandardCrosswalk=FALSE
    useStandardCrosswalk = FALSE,
    # TRUE if prepping data for EIAplantAssociation and/or condenserDuty
    # packages
    prepCondenserDuty = TRUE,
    # only required if prepCondenserDuty = TRUE
    eia_year = 2020
  )
```

The user should repeat the steps: (1) run `import_EIAData()`, and (2)
resolve highlighted values in the crosswalk, until a list object is
returned by the function. The list object will contain all tables
found in the `scriptTableName` column of the crosswalk, and all column
names found in `InputColumnNames` will have been changed to
`scriptColnames`. If values appear in the `scriptImportFunc` column,
those functions will have been run on the data to further format it
for analysis.

It is recommended that the user save the completed crosswalk for
future use. Each time the user needs to access the formatted data,
the `import_EIAData()` function can be used with the existing
completed crosswalk, and since the crosswalk is complete no
highlighted values will need to be resolved. The user can also use
the `*.csv` files saved if `outputCSV = TRUE`.

### Section 2.4.2: Run `import_EIAData()` Using an Existing Saved Crosswalk
When using a user developed, saved crosswalk, there are a few
requirements:

1. The file *must* be in .xlsx format;
2. All of the columns listed as a "Required Column" in Table 1 *must*
   be present;
3. All `scriptImportFunc` values *must* be names of functions
   available in the user's R environment;
4. If developing a crosswalk for use in the EIAplantAssociation
   and/or condenserDuty packages, all `scripTableName`,
   `scriptColnames`, and `scriptImportFunc` values found in the
   `crosswalk2015` data object *must* be present, with the exception
   of values found in Table 2.

To run `import_EIAData()` on an existing crosswalk, use the code below:

```{r, eval=FALSE, echo=TRUE}
# run the import_EIAData() function for the first time using the
# crosswalk2015 object

# path to crosswalk being used to start
path_InputData_Metafile <-
  paste0(repoPath, "./newCrosswalk2020.xlsx")

# path to EIA raw data
#
# path should be to directory with extracted data from ZIP files
# (created by eia_webpull)
path_EIAInputData <- paste(EIAyearSave, eia_year, sep = "/")

# if saving formatted tables as CSV set outputCSV <- TRUE; otherwise
# outputCSV <- FALSE
outputCSV <- TRUE

# path to save formatted tables in CSV form (set
#
# path_outputCSV <- NA, if outputCSV <- FALSE)
path_outputCSV <- path_EIAInputData

# execute import_EIAData for every time except the first time
inputData.list <-
  import_EIAData(path_InputData_Metafile,
    path_EIAInputData,
    outputCSV,
    path_outputCSV,
    # TRUE if prepping data for EIAplantAssociation and/or
    # condenserDuty packages
    prepCondenserDuty = TRUE,
    # only required if prepCondenserDuty = TRUE
    eia_year = 2020
  )
```

If the crosswalk is complete, the `import_EIAData()` function will
return a list object that will contain all tables found in the
`scriptTableName` column of the crosswalk, and all column names found
in `InputColumnNames` will have been changed to `scriptColnames`. If
values appear in the `scriptImportFunc` column, those functions will
have been run on the data to further format it for analysis.

If the crosswalk contains references to data that cannot be found in
`path_EIAInputData`, the `import_EIAData()` function will return the
following:

```
> inputData.list<-import_EIAData(path_InputData_Metafile,path_EIAInputData,outputCSV,path_outputCSV)
[1] "Please review the Input Data Metafile for highlighted errors."
```

In this case, the `import_EIAData()` function has modified the
crosswalk to highlight data that it was unable to find in
`path_EIAInputData` and saved the resulting file to the location
specified by `path_InputData_Metafile`. The `import_EIAData()`
function works from left to right attempting to match what is in the
crosswalk to what is in the `path_EIAInputData` directory. With each
run of `import_EIAData()` the user should open and resolve all
highlighted values. For example, if running 2020 in preparation for
the EIAplantAssociation and/or condenserDuty packages, and the
`scriptTableName` is `bogen`, and the value in the `InputFile` column
is `6_1_EnviroAssoc_Y2015.xlsx`, it will be highlighted because it
cannot be found in the 2020 data. The user should look at the
`InputSheetDescription` and attempt to locate the data within the
`path_EIAInputData` directory where the 2020 data is stored. In the
case of 2020, the `InputFile` value should be changed to
`6_1_EnviroAssoc_Y2020.xlsx` for the `scriptTableName` `bogen`, but
for the year 2008, the `InputFile` would be `F860_SCHEDULE6_Y08.xls`.
All `InputFile` values should be present in the `path_EIAInputData`
directory.

The user should repeat the steps: (1) run `import_EIAData()` and (2)
resolve highlighted values in the crosswalk, until a list object is
returned by the function. The list object will contain all tables
found in the `scriptTableName` column of the crosswalk, and all column
names found in `InputColumnNames` will have been changed to
`scriptColnames`. If values appear in the `scriptImportFunc` column,
those functions will have been run on the data to further format it
for analysis.

It is recommended that the user save the completed crosswalk for
future use. Each time the user needs to access the formatted data,
the `import_EIAData()` function can be used with the existing
completed crosswalk, and since the crosswalk is complete no
highlighted values will need to be resolved. The user can also use
the `*.csv` files saved if `outputCSV = TRUE`.

### Section 2.4.3: Run `import_EIAData()` for Use Outside of the EIAplantAssociation and condenserDuty Packages
The `import_EIAData()` function is flexible enough to format data
according to the user's needs. When creating a crosswalk for use
outside of the EIAplantAssociation and condenserDuty packages, it
is important to remember the following requirements:

1. The file *must* be in .xlsx format;
2. All the columns listed as a `Required Column` in Table 1 *must* be
   present;
3. All `scriptImportFunc` values *must* be names of functions
   available in the user's R environment.

When building a custom crosswalk, it is important to remember the
function of each column in the crosswalk. Refer to the documentation
for the `crosswalk2015` data object using the following:

```{r, eval=FALSE,echo=TRUE}
?importThermoEIA::crosswalk2015
```

Remember, all columns of a given table will be imported, but only
those listed in `InputColumnName` will have there headers replaced
with values in `scriptColnames`.

The process to build a custom crosswalk is the same as the process
detailed in [Section
2.4.2](#section-2.4.2-run-import_eiadata-using-an-existing-saved-crosswalk)
with the exception of the `prepCondenserDuty` and `eia_year`
arguments. If the data is to be formatted for use outside of the
EIAplantAssociation and/or condenserDuty packages, `prepCondenserDuty`
should be set to `FALSE`. The `eia_year` argument will be ignored if
`prepCondenserDuty` is `FALSE`.

# Section 3: Resources for EIA Data Identification
Below is a table of helpful resources when analyzing EIA
thermoelectric plant data. The answer to most questions about the EIA
data used by the EIAplantAssociation and condenserDuty packages is
found in this table:

```{r eval=TRUE,echo=FALSE}
table4 <- structure(list(URL = c(
  "[Guide to EIA Electric Power](https://www.eia.gov/electricity/data/guide/pdf/guide.pdf)",
  "[EIA Technical Notes](https://www.eia.gov/electricity/annual/pdf/tech_notes.pdf)",
  "[EIA Survey](https://www.eia.gov/Survey/)",
  "[EIA Glossary](https://www.eia.gov/tools/glossary/)",
  "[Form EIA-860 Data](https://www.eia.gov/electricity/data/eia860/)",
  NA, "[OMB Report Form EIA-860](https://omb.report/icr/202211-1905-001/doc/126698100)",
  "[Form EIA-860 Instructions](https://omb.report/icr/202112-1905-001/doc/117324201)",
  "[Form EIA-923 Data](https://www.eia.gov/electricity/data/eia923/)",
  "[EIA Form-923 Reporting Form](https://www.eia.gov/survey/form/eia_923/form.pdf)",
  "[Form EIA-923 Instructions](https://www.eia.gov/survey/form/eia_923/instructions.pdf)",
  "[Form EIA-923 8D Instructions](https://www.eia.gov/survey/form/eia_923/instructions_schedule8d.pdf)",
  "[Form EIA-767 Instructions](https://www.eia.gov/survey/form/eia_767/instructions_form.pdf)",
  "[Form EIA-906 Instructions](https://www.eia.gov/survey/form/eia_906/instructions_form.pdf)",
  "[Form EIA-920 Instructions](https://www.eia.gov/survey/form/eia_920/instructions_form.pdf)",
  "[EIA Thermoelectric cooling water data](https://www.eia.gov/electricity/data/water/)",
  "[EIA-EPA Data Crosswalk](https://www.epa.gov/airmarkets/power-sector-data-crosswalk)",
  "[Boiler Generator Associations](https://catalyst.coop/2018/08/07/boiler-generator-associations/)",
  "[Synapse Interactive Map of Power Plants](https://www.synapse-energy.com/tools/interactive-map-us-power-plants)",
  "[ArcGIS Interactive Map of Power Plants](https://www.arcgis.com/apps/dashboards/201fc98c0d74482d8b3acb0c4cc47f16)"
), `EIA Form` = c(
  "all", "all", NA, NA, "860", "860", "860", "860",
  "923", "923", "923", "923", "767", "906", "920", NA, "all", NA,
  NA, NA
), File = c(
  NA, NA, NA, NA, NA, "LayoutY2015.xlsx", NA,
  NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA, NA
), Description = c(
  "2018 high-level discussion of 860, 923, and other forms",
  "2022 technical notes on 860, 923, and other forms",
  "Lists all EIA forms including discontinued forms",
  "Glossary of technical terms and agency terminology",
  "Current and past data download, plus high-level overview; The 860 is a year-end status report on installed equipment at power plants",
  "Brief description of each data element in the 2015 EIA 860; tables provide meaning of short alphabetic codes",
  "Online reporting form; 2022 revision",
  "Reporting instructions",
  "Download site for 923 data",
  "923 form",
  "Instructions for 2023 EIA form 923",
  "Instructions for section 8D, cooling water use, with happy cartoons",
  "Instructions for 767 form in 2005, precursor of 860 and 923 form",
  "Instructions for 906 form in 2007, precursor of 923 form",
  "2004/2005 form 920 instructions, precursor of 923 form",
  "2014-2020 Summary of water use, not the same as section 8D of 923 form; includes gross generation.",
  "EPA-EIA power sector data crosswalk, October 2022",
  "Non-EIA analysis of boiler-generator associations, cite as Gosnell 2018",
  "Nice interactive map of power plants by capacity and type",
  "Nice interactive map of power plants by capacity and type"
)), row.names = c(
  NA,
  20L
), class = "data.frame")

table4$`EIA Form` <- ifelse(is.na(table4$`EIA Form`), "", table4$`EIA Form`)
table4$File <- ifelse(is.na(table4$File), "", table4$File)
table4$URL <- ifelse(is.na(table4$URL), "", table4$URL)

knitr::kable(
  table4,
  caption = paste0(
    "Table 4: Helpful Resources for Analysis of EIA Thermoelectric ",
    "Plant Data"
  )
)
```

## Acknowledgements
