---
title: "towerWaterUse"
author: "Kenneth Skinner, ..."
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
    toc: true
vignette: >
  %\VignetteIndexEntry{Vignette Title}
  %\VignetteEngine{knitr::knitr}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


# Section 1 : The towerWaterUse package

Description of the towerWaterUse package

## Example links

This is how you create a link to an external URL

[dplyr](https://cran.r-project.org/web/packages/dplyr/index.html)

This is  how you link to a specific part of the vignette
[Go To Referenced Section](#now-you-are-at-referenced-section)



## Example R code chunks

To show code but not evaluate

```{r, echo=TRUE, eval=FALSE}
#install the remotes package (one-time process)
install.packages("remotes")

#install the importThermoEIA package (one-time process)
remotes::install_github(repo="https://github.com/rniswon/Thermoelectric",
                        subdir="importThermoEIA",build_vignettes = T,upgrade = "never")

#load the importThermoEIA package (necessary each time the package is used in a given R session)
library(importThermoEIA)
```

To show code and evaluate

```{r, echo=TRUE, eval=TRUE}
cat("Hello")
```

To evaluate and NOT show code

```{r, echo=FALSE,eval=TRUE}
cat("This is output I want as exceuted by R")
```

## To Create a table

```{r,eval=TRUE,echo=FALSE}
myTable<-data.frame(column1 = c(1,2,3),myotherColumn = c(2,3,4))
knitr::kable(myTable,caption = "Table 1: this is my table caption") 
```

## To format text

<span style="color: red;">This text is red</span>

*This Text is italics*

**This text is bold**

[This link has cheatsheet for text style](https://www.markdownguide.org/cheat-sheet/)

## Now you are at referenced section

This is the section that you linked to in [Example Links](#example-links)

## how to add a data object to your package

First have the data object in your environment and named as you want it to be imported.  Then save it to the data directory like this

```{r,eval=FALSE,echo=TRUE}
#any type of R data object can be saved, does NOT have to be a data.frame
#this is just an example
myDataObject<-data.frame(x=c(1,2,3),y=c(2,3,4))

#save the data to the package
save(myDataObject,file="./towerWaterUse/data/myDataObject.rda")

```

Then you need to document the data object by going to File>New File>R Documentation and naming your data object and selecting dataset.  This will build a template like [Documentation for data object in importThermoEIA-package](https://github.com/rniswon/Thermoelectric/blob/master/importThermoEIA/man/crosswalk2015.rd).  Fill out the documentation file for your data object and save it to the ./towerWaterUse/man directory.

## R functions

Scripts will need to be converted to functions with arguments that cover all required input fields

If I had a script that look like this

```{r eval=FALSE,echo=TRUE}
#note the use of the packagename::functionname syntax, this is REQUIRED
myDataObject<-myDataObject %>% dplyr::mutate(y=y^2)
firstElementOfVector<-1

outputVector<-firstElementOfVector
for (i in 1:nrow(myDataObject)){
  out<-myDataObject[i,]$y
  outputVector<-c(outputVector,out)
}

#outputVector is the goal of the script

```

I could convert it to a function like this

```{r eval=FALSE,echo=TRUE}

myFunc<-function(firstElementOfVector = 1){#firstElementOfVector is input argment, 1 is defualt but could be anything.
  
  #load data object
  data("myDataObject")
  myDataObject<-myDataObject %>% dplyr::mutate(y=y^2)

outputVector<-firstElementOfVector
for (i in 1:nrow(myDataObject)){
  out<-myDataObject[i,]$y
  outputVector<-c(outputVector,out)
}
  
  return(outputVector)#this is what the function will output
}

```

Functions should be documented in standard roxygen/rmarkdown style.  See [Function from importThermoEIA-package](https://github.com/rniswon/Thermoelectric/blob/master/importThermoEIA/R/import_EIAData.R)  The documentation is at the top.  Function examples must be runable without anything extra.

Function documentation needs to be converted to help files this way

```{r, echo=TRUE, eval=FALSE}
roxygen2::roxygenise("./towerWaterUse",clean=T)
#this will generate your NAMESPACE file and all function documentation
#also creates top level pacakge documentation
```

## Top level Package documentation 

In addition to the vignette there should be a top level package documentation.  Template is here ./towerWaterUse/R/towerWaterUse-package.R

## Edit the DESCRIPTION file

Add to the Depends: section all dependency packages
Do NOT delete magrittr from Imports:

## Using the pipe (%>%) in your package

Since most people use this I went a head and added the required stuff for that to work.  Including adding magrittr to the DESCRIPTION file and the utils-pipe.R function in the R directory which creates the pipe.Rd file in the man directory when roxygen2::roxygenise() is run.  Do not delete these elements unless your package NEVER uses pipe.

## creating Unit tests

If you want to go into this, check the structure in here https://github.com/rniswon/Thermoelectric/tree/master/importThermoEIA/tests
I can also help with this step.

## to test and build your package

Go to Build in Rstudio and Configure Build Tools set the package directory to towerWaterUse.  Then you can Click Build>BuildSourcePackage
CLOSE Rstudio
Go to Tools>InstallPackages and select the towerWaterUse_1.0.tar.gz file created with Build Source Package
Your package will then be loaded and you can use 

```{r eval=FALSE,echo=TRUE}
library(towerWaterUse)
?`towerWaterUse-package` #displays top level package documentation
??towerWateruse  #displays everything related to your package including vignettes
?myFunc #displays help file for your function called "myFunc" (replace with your function names)
```